\documentclass[]{report}
\usepackage{amssymb}
\title{\textbf{\LARGE Introduction to a PWA}}
\author{\textbf{\LARGE Roque Vargas Luis Roberto}}
\begin{document}
\maketitle
\begin{flushleft}
    \textbf{\LARGE What is a PWA?}
\end{flushleft}
\begin{flushleft}
    \textbf{It is a web application that combines features of a browser and can use mobile functionalities. PWAs can be accessed from any browser and can be downloaded like a native app.}
\end{flushleft}
\begin{flushleft}   
    \textbf{\LARGE Characteristics of a PWA}
\end{flushleft}
\begin{flushleft}
    \begin{itemize}
        \item Updated: PWAs always show the latest version to the user, using automatic updates constantly without the need for manual downloads.
        \item Secure: As they have web characteristics, they use the HTTPS protocol, providing an additional level of security using technologies like TLS.
        \item Fast: They have the loading speed of a browser, optimization, and caching to accelerate the search process.
        \item Offline: They can function without the internet, allowing pages to be loaded for users and informing them that there is no current connection, enhancing the user experience.
    \end{itemize}
\end{flushleft}
\begin{flushleft}
    \textbf{\LARGE Differences between a native, responsive, and progressive web}
\end{flushleft}
\begin{center}
    \begin{tabular}{c | c | c | c} 
        Features & Native Web & Responsive Web & Progressive Web\\
        Offline Functionality & \checkmark & $\times$ & \checkmark \\
        Push Notifications & \checkmark & $\times$ & \checkmark \\
        Installable on Home Screen & \checkmark & $\times$ & \checkmark \\
        No Installation Required & $\times$ & \checkmark & \checkmark \\
        No Update Required & $\times$ & \checkmark & \checkmark \\
        Works on All Devices & $\times$ & \checkmark & \checkmark \\
    \end{tabular}
\end{center}

\vspace{4em} 
\newpage

\begin{flushleft}   
    \textbf{\LARGE Advantages}
\end{flushleft}
\begin{flushleft}
    \begin{itemize}
        \item Cross-platform, accessible from any browser and operating system.
        \item Adapts functions to the user's browser.
        \item Allows informing users through push notifications.
        \item No need for downloads, saving space on the mobile device.
        \item Loading speed is similar to native apps, superior to web applications.
    \end{itemize}
\end{flushleft}
\begin{flushleft}   
    \textbf{\LARGE Disadvantages}
\end{flushleft}
\begin{flushleft}
    \begin{itemize}
        \item Cannot access all device functionalities, such as contact lists or advanced camera features.
        \item Currently, not all browsers are compatible with PWAs, so a portion of users may still not have access to them.
        \item PWAs are suitable for developing mobile-friendly and accessible apps, but their technology may not yet support creating very complex sites.
    \end{itemize}
\end{flushleft}
\begin{flushleft}
    \textbf{\LARGE References}
\end{flushleft}
\begin{flushleft}
    \begin{itemize}
        \item Contacto. (2023, May 12). What is PWA: main functions and characteristics - IMMUNE. Immune Technology Institute. https://immune.institute/blog/que-es-pwa/
        \item Herrera, I., Herrera, I. (2023, July 27). Advantages and disadvantages of PWAs. ttandem.com. https://www.ttandem.com/blog/desarrollo-que-son-las-pwa-o-progressive-web-applications/ventajas-y-desventajas-de-las-pwa/
        \item Mora, S. L. (2022, October 4). What is PWA: features, technologies, advantages, and disadvantages. DIGITAL55. https://digital55.com/blog/que-es-pwa-ventajas-desventajas/
        \item Vidal, M. (2022, November 2). PWA: What are Progressive Web Apps and how do they work. Thinking for Innovation. https://www.iebschool.com/blog/progressive-web-apps-analitica-usabilidad/
    \end{itemize}
\end{flushleft}
\end{document}
